### 2024-05-16 intro.qmd
20240516 - convert "class"/"course" to "book"

Of course, this is not a traditional psychology textbook.
However, the class incorporates important psychological concepts, such as cognitive biases in judgment and prediction, etc.
In the modern world of big data, research and society need people who know how to make sense of the information around us.
Psychology is in a prime position to teach applied statistics to a wide variety of students, most of whom will not have careers as psychologists.
Psychology can teach the importance of statistics given humans' cognitive biases.
It can also teach about how these biases can influence how people interpret statistics.
This course will teach readers the applications of statistics (prediction) and research methods (empiricism) to answer questions they find interesting, while applying scientific and psychological rigor.

>>>>

Of course, this is not a traditional psychology textbook.
However, the book incorporates important psychological concepts, such as cognitive biases in judgment and prediction, etc.
In the modern world of big data, research and society need people who know how to make sense of the information around us.
Psychology is in a prime position to teach applied statistics to a wide variety of students, most of whom will not have careers as psychologists.
Psychology can teach the importance of statistics given humans' cognitive biases.
It can also teach about how these biases can influence how people interpret statistics.
This book will teach readers the applications of statistics (prediction) and research methods (empiricism) to answer questions they find interesting, while applying scientific and psychological rigor.
